{\bf {\Large Improving estimates of ecosystem metabolism computed from dissolved oxygen time series}}

### 2014-11-24 swmp_noise.Rnw
revisions that include sun and tide angle diagnostics

p1 <- ggplot(to_plo, aes(x = factor(err_rng_pro), y = factor(err_rng_obs), z = cor, fill = cor)) + 
  geom_tile() +
  facet_grid(bio_rng ~ tide_assoc,
    labeller = plot_labeller) +
  scale_fill_gradientn(name = 'Correlation', 
    colours = brewer.pal(11, 'Spectral')#, limits = c(0, 1)
    ) +
  scale_x_discrete(expand = c(0,0)) + 
  scale_y_discrete(expand = c(0,0)) +
  xlab(expression(italic(epsilon [pro]))) +
  ylab(expression(italic(epsilon [obs]))) + 
  theme_bw() +
  mat_theme

p2 <- ggplot(to_plo, aes(x = factor(err_rng_pro), y = factor(err_rng_obs), z = err, fill = err)) + 
  geom_tile() +
  facet_grid(bio_rng ~ tide_assoc,
    labeller = plot_labeller) +
  scale_fill_gradientn(name = 'RMSE', 
    colours = rev(brewer.pal(11, 'Spectral')), limits = c(0.6, 1.8)
    ) +
  scale_x_discrete(expand = c(0,0)) + 
  scale_y_discrete(expand = c(0,0)) +
  xlab(expression(italic(epsilon [pro]))) +
  ylab(expression(italic(epsilon [obs]))) + 
  theme_bw() +
  mat_theme

@@

@@

p1 <- ggplot(to_plo, aes(x = factor(dec_time), y = factor(hour), z = cor, fill = cor)) + 
  geom_tile() +
  facet_grid(~ Tide) +
  scale_fill_gradientn(name = 'Correlation', 
    colours = brewer.pal(11, 'Spectral')#, limits = c(0.3, 0.7),
#     breaks = seq(0.3, 0.7, by = 0.1)
    ) +
  scale_x_discrete(expand = c(0,0)) +
  scale_y_discrete(expand = c(0,0)) +
  xlab('Days') +
  ylab('Hours') + 
  theme_bw() +
  mat_theme

p2 <- ggplot(to_plo, aes(x = factor(dec_time), y = factor(hour), z = err, fill = err)) + 
  geom_tile() +
  facet_grid(~ Tide) +
  scale_fill_gradientn(name = 'RMSE', 
    colours = rev(brewer.pal(11, 'Spectral')), limits = c(0.6, 1.8) 
#     labels = format(seq(1, 1.5, by = 0.1), nsmall = 1)
    ) +
  scale_x_discrete(expand = c(0,0)) + 
  scale_y_discrete(expand = c(0,0)) +
  xlab('Days') +
  ylab('Hours') + 
  theme_bw() +
  mat_theme

@@

@@

@@

cap.val<-'Correlations of tidal changes at each site with continuous \\ac{DO} observations and metabolism estimates (gross production, respiration, and net metabolism) before (observed) and after (filtered) filtering with weighted regression.  Values are averages of monthly correlations.  \\ac{DO} values are correlated with predicted tidal height at each observation, whereas metabolism estimates are correlated with mean tidal height change between observations during day, night, or total day periods for production, respiration, and net metabolism, respectively.'

@@

latex( 
  tab,
  file = '',
  rowlabel = 'Site',
  rgroup = unique(rows), 
  n.rgroup = rep(2, 4),
  insert.bottom = foot.val,
  caption = cap.val,
  colheads = c('DO', 'Pg\\textsuperscript{\\textit{a}}', 'Rt', 'NEM'),
  caption.loc = 'top',
  rowname = rep(c('Observed', 'Filtered'), 4),
  label = 'tab:cor_res'
  )

@@

@@

tab <- form_fun(to_tab[, -c(1:2)])
rows <- to_tab[, 2]
cap.val<-'Summary of metabolism estimates (gross production, respiration, and net metabolism) for case studies using \\ac{DO} time series before (observed) and after (filtered) filtering with weighted regression.  Means and standard errors are based on daily integrated metabolism estimates.  Anomalous values are the proportion of metabolism estimates that were negative for gross production and positive for respiration.  Results are for weighted regressions with half window widths of six days, one hour within each day, and a tidal height proportion of one half.'

foot.val<-'\\textsuperscript{\\textit{a}}Pg: gross production, Rt: respiration, NEM: net ecosystem metabolism' 
latex( 
  tab,
  file = '',
  rowlabel = 'Site',
  insert.bottom = foot.val,
  caption = cap.val,
  caption.loc = 'top',
  rgroup = unique(to_tab$Site),
  n.rgroup = rep(2, 4),
  cgroup = c('Pg\\textsuperscript{\\textit{a}}', 'Rt', 'NEM'),
  n.cgroup = c(3, 3, 2),
  rowname = rows,
  colheads=c(rep(c('Mean','Std. Err.', 'Anom'),2), c('Mean', 'Std. Err.')),
  label = 'tab:case_res'
  )
@

>>>>

p1 <- ggplot(to_plo, aes(x = factor(err_rng_pro), y = factor(err_rng_obs), z = cor, fill = cor)) + 
  geom_tile() +
  facet_grid(bio_rng ~ tide_assoc,
    labeller = plot_labeller) +
  scale_fill_gradientn(name = 'Correlation', 
    colours = brewer.pal(11, 'GnBu')#, limits = c(0, 1)
    ) +
  scale_x_discrete(expand = c(0,0)) + 
  scale_y_discrete(expand = c(0,0)) +
  xlab(expression(italic(epsilon [pro]))) +
  ylab(expression(italic(epsilon [obs]))) + 
  theme_bw() +
  mat_theme

p2 <- ggplot(to_plo, aes(x = factor(err_rng_pro), y = factor(err_rng_obs), z = err, fill = err)) + 
  geom_tile() +
  facet_grid(bio_rng ~ tide_assoc,
    labeller = plot_labeller) +
  scale_fill_gradientn(name = 'RMSE', 
    colours = rev(brewer.pal(11, 'GnBu')), limits = c(0, 2.5)
    ) +
  scale_x_discrete(expand = c(0,0)) + 
  scale_y_discrete(expand = c(0,0)) +
  xlab(expression(italic(epsilon [pro]))) +
  ylab(expression(italic(epsilon [obs]))) + 
  theme_bw() +
  mat_theme

@@

options(digits=3)

@@

p1 <- ggplot(to_plo, aes(x = factor(dec_time), y = factor(hour), z = cor, fill = cor)) + 
  geom_tile() +
  facet_grid(~ Tide) +
  scale_fill_gradientn(name = 'Correlation', 
    colours = brewer.pal(9, 'GnBu'),
    labels = format(seq(0.62, 0.7, by = 0.02), nsmall = 1),
    limits = c(0.62, 0.7),
    breaks = seq(0.62, 0.7, by = 0.02)
    ) +
  scale_x_discrete(expand = c(0,0)) +
  scale_y_discrete(expand = c(0,0)) +
  xlab('Days') +
  ylab('Hours') + 
  theme_bw() +
  mat_theme

p2 <- ggplot(to_plo, aes(x = factor(dec_time), y = factor(hour), z = err, fill = err)) + 
  geom_tile() +
  facet_grid(~ Tide) +
  scale_fill_gradientn(name = 'RMSE', 
    colours = rev(brewer.pal(9, 'GnBu')), 
    labels = format(seq(1.08, 1.2, by = 0.04), nsmall = 1),
    limits = c(1.08, 1.2),
    breaks = seq(1.08, 1.2, by = 0.04)
    ) +
  scale_x_discrete(expand = c(0,0)) + 
  scale_y_discrete(expand = c(0,0)) +
  xlab('Days') +
  ylab('Hours') + 
  theme_bw() +
  mat_theme

@@

options(digits=1)
@
\vfill
\clearpage

@@

% moving correlations
\centering\vspace*{\fill}
<<move_corrs, cache = T, fig.height = 5, fig.width = 5.5, out.width = '0.8\\textwidth', eval = T, echo = F, fig.cap = 'Correlations of sun angle with tidal change (as an angular rate) using a half-window width of 12 days.  Correlations larger or smaller than zero are periods when weighted regression may not effectively quantify variation from biological and physical sources in \\ac{DO} time series due to collinearity.'>>=
######
load('angle_tide_its.RData')

tmp <- do.call('cbind', angle_tide_its)

# file to upload, doesn't matter which for dates
load(paste0('wtreg/ELKVM_wtreg_1.RData'))
dat <- get(gsub('\\.RData$', '', 'ELKVM_wtreg_1.RData'))

tmp <- data.frame(DateTimeStamp = dat$DateTimeStamp, tmp)
tmp <- melt(tmp, id.var = 'DateTimeStamp')
tmp$daywin <- gsub('^X|\\..*$', '' ,tmp$variable)
tmp$case <- gsub('^X[0-9]*\\.', '', tmp$variable)

# show 12 day half window
daywin <- '12'
to_plo <- tmp[tmp$daywin %in% daywin, ]

my_theme <- theme(
  legend.position = 'top',
  axis.title.x = element_blank(),legend.box= 'horizontal',
  plot.margin= unit(c(0, 1, 0, 1), "lines") # top right bottom left
  )

# plot
p1 <- ggplot(to_plo, 
    aes(x = DateTimeStamp, y = value)) + 
  geom_line() + 
  facet_wrap(~ case, ncol = 1) + 
  theme_bw() + 
  ylab('Correlation') +
  scale_y_continuous(limits= c(-0.5, 0.5)) +
  geom_hline(yintercept = 0, linetype = 'dashed', colour = 'red') +
  my_theme

@@

# remove NEM
tab <- tab[, !names(tab) %in% 'NEM']

cap.val<-'Correlations of tidal changes at each site with continuous \\ac{DO} observations and metabolism estimates (gross production, respiration) before (observed) and after (filtered) filtering with weighted regression.  Values are averages of monthly correlations.  \\ac{DO} values are correlated with predicted tidal height at each observation, whereas metabolism estimates are correlated with mean tidal height change between observations during day or night periods for production and respiration, respectively.'

@@

latex( 
  tab,
  file = '',
  rowlabel = 'Site',
  rgroup = unique(rows), 
  n.rgroup = rep(2, 4),
  insert.bottom = foot.val,
  caption = cap.val,
  colheads = c('DO', 'Pg\\textsuperscript{\\textit{a}}', 'Rt'),
  caption.loc = 'top',
  rowname = rep(c('Observed', 'Filtered'), 4),
  label = 'tab:cor_res'
  )

@@

# remove NEM columns
to_tab <- to_tab[, !grepl('^NEM', names(to_tab))]

@@

tab <- form_fun(to_tab[, -c(1:2)])
rows <- to_tab[, 2]
cap.val<-'Summary of metabolism estimates (gross production, respiration) for case studies using \\ac{DO} time series before (observed) and after (filtered) filtering with weighted regression.  Means and standard errors are based on daily integrated metabolism estimates.  Anomalous values are the proportion of metabolism estimates that were negative for gross production and positive for respiration.'

foot.val<-'\\textsuperscript{\\textit{a}}Pg: gross production, Rt: respiration' 
latex( 
  tab,
  file = '',
  rowlabel = 'Site',
  insert.bottom = foot.val,
  caption = cap.val,
  caption.loc = 'top',
  rgroup = unique(to_tab$Site),
  n.rgroup = rep(2, 4),
  cgroup = c('Pg\\textsuperscript{\\textit{a}}', 'Rt'),
  n.cgroup = c(3, 3),
  rowname = rows,
  colheads=c(rep(c('Mean','Std. Err.', 'Anom'),2), c('Mean', 'Std. Err.')),
  label = 'tab:case_res'
  )
@
